The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-29 paper/paper.tex
paper: strip last column in comparison table

\begin{tabularx}{\linewidth}{lYcYYYl}
  \toprule
  arity                     & formalisation style          & iteration                       & relevance                     & structure          & name of semantics   \\
  \midrule
  \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & predicate          & reducibility        \\
                            &                              &                                 & relevant                      & family             &                     \\
                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}              &                                          \\
                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & subobject          &                     \\
                            &                              &                                 & relevant                      & fibration          &                     \\
                            &                              & \multicolumn{2}{l}{iterated}    & augmented semi-simplicial set &                                          \\
  \midrule
  \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & relation           & logical relation    \\
                            &                              &                                 & relevant                      & correspondence     &                     \\
                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}              &                                          \\
                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & fibered relation ? &                     \\
                            &                              &                                 & relevant                      & span               &                   & \\
                            &                              & \multicolumn{2}{l}{iterated}    & semi-cubical set              &                                          \\
  \bottomrule
\end{tabularx}

>>>>

\begin{tabularx}{\linewidth}{lYcYYl}
  \toprule
  arity                     & formalisation style          & iteration                       & relevance                     & logical structure    \\
  \midrule
  \multirow{6}{1cm}{unary}  & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & predicate            \\
                            &                              &                                 & relevant                      & family               \\
                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & subobject            \\
                            &                              &                                 & relevant                      & fibration            \\
                            &                              & \multicolumn{2}{l}{iterated}    & augmented semi-simplicial set                        \\
  \midrule
  \multirow{6}{1cm}{binary} & \multirow{3}{1.5cm}{indexed} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & relation             \\
                            &                              &                                 & relevant                      & correspondence       \\
                            &                              & \multicolumn{2}{l}{iterated}    & \emph{this work}                                     \\
                            & \multirow{3}{1.5cm}{fibered} & \multirow{2}{2cm}{non-iterated} & proof-irrelevant              & fibered relation ?   \\
                            &                              &                                 & relevant                      & span               & \\
                            &                              & \multicolumn{2}{l}{iterated}    & semi-cubical set                                     \\
  \bottomrule
\end{tabularx}
